COG-ED Manuscript

### 2021-08-16 06_Paper/COG-ED/Manuscript.Rmd
Finished introduction

The present study contributes to the investigation of effort and SVs by changing one fundamental assumption of the original COG-ED paradigm: The assumption that the easiest n-back level has the highest SV.

-	higher n-back levels and more difficult signal-to-noise audio comprehension task levels are discounted in similar ways in the COG-ED paradigm -> doesn’t just work for n-back (Crawford et al., 2021)
-	there are strong within-subjects associations of the SV of different cognitive domains, i.e. n-back and audio comprehension, even after controlling for performance d’, and even though the audio task was rated as less mentally demanding and effortful (Crawford et al., 2021)

Justifying changes in the COG-ED procedure:
-	subjective values did not decline between n=4 and n=5 (Culbreth et al., 2016) -> n=5 is too universally difficult to be valid
-	only higher n-back levels are reliable for performance computation (Jaeggi et al., 2010) -> we will not include n = 1 in our performance measure

>>>>

The present study contributes to the investigation of effort and SVs by changing one fundamental assumption of the original COG-ED paradigm: The assumption that the easiest n-back level has the highest SV.
We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer 1-back.
In fact, our COG-ED adaptation allows the computations of SVs, even if the individual does not have a clear preference for one task level.
In the present study, we will validate this adaptation by replicating the findings of Westbrook et al. [-@Westbrook2013].
Additionally, we will apply the adaption to a task with different emotion regulation strategies to establish an effort discounting paradigm for task varieties that have no objective order of task load.
The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but it has not been applied to tasks without objective task load so far.
